Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-04-26 paper/paper.tex
Working on TabShots section
Mainly finished with description, need evaluation, pros and cons.

When any tab regains focus, TabShots compares a new screenshot of the tab and it's current favicon to the most recent stored screenshot and favicon that was recorded before the tab lost focus.  The small favicons are compared by source, and the screenshots are compared in a visually divided manner using the HTML5 canvas element.  The screenshots are divided in a raster of fixed-size tiles, and each tile in the new screenshot is compared to the most recently stored screenshot of the tab.  If the tiles do not match exactly, that area is marked as changed.  The HTML5 canvas element provides powerful image manipulation capabilities that allowed the rastering and comparison algorithms to be implemented.

@@

>>>>

When any tab regains focus, TabShots compares a new screenshot of the tab and it's current favicon to the most recent stored screenshot and favicon that was recorded before the tab lost focus.  The small favicons are compared by source, and the screenshots are compared in a visually divided manner using the HTML5 canvas element.  The screenshots are divided in a raster of fixed-size tiles, and each tile in the new screenshot is compared to the most recently stored screenshot of the tab.  The tiles are sized as 10x10 pixels, which are deemed by the authors as a balance between performance and precision.  If the tiles do not match exactly, that area is marked as changed.  The HTML5 canvas element provides powerful image manipulation capabilities that allowed the rastering and comparison algorithms to be implemented.

@@

Finally, there is also an intended component for blacklisting sites that have confirmation of tabnabbing attempts.  The developers have created an optaionl server-side component which can pull reported URLs from individual users, and add the confirmed URLs to a database.  If the user decides that the current page is attempting tabnabbing and provides their explicit approval, the application can be signaled to send the accused page's URL, the image before the user switched tabs, and the image of the page after the user switched tabs.  The server-side application uses its own automated comparison process and the further verification of a human analyst to decide if the page is indeed a phishing page, and whether the URL should be added to a subscription model blacklist.
